Graphs of Mice and Men

### 2016-07-02 Paper/Draft.tex
Added almost all results

 \section*{Summary}
 %TODO Definitions
 %TODO Word index
 %TODO Fix hoofdletters (bv ontology, kb)
 %TODO spelling (database dataset)
 %TODO volgorde bieb (APA?)
 %TODO Results interpretation: uitleg waarom hoger en lager
 %TODO Plaatje VOWL
 %TODO Verbeteringen discussieren
 %TODO Verwijder ensemble uit evaluation
 %TODO F-measure aan evluation
 \tableofcontents
 \newpage

@@

  \begin{figure}
  \includegraphics[width=0.7\textwidth]{vowlview}
  \caption[]{}
  \label{vowlfig}
  \end{figure}

@@

  \subsection{F-score}
  \begin{table}[H]
  \caption[$F_1$ mice]{The $F_1$-scores for the different matchers for the mice dataset compared to the result of AML at OAEI 2015 \cite{oaei2015}}
  \label{fscores}
  \begin{tabular}{l|ll}
  \multirow{2}{*}{\textbf{Matcher}} & \multicolumn{2}{c}{\textbf{$F_1$-score}} \\
  & Anatomy & Medical\\
  \hline
  Alternative & 0.6372 & 0.2494 \\
  Bidirectional & 0.8432 & 0.4946 \\
  Label match + Random & 0.6926 & 0.3875 \\
  Generic & 0.6372 & 0.2419 \\
  \textbf{AML} & \textbf{0.94} & \textbf{0.81} \\ %http://disi.unitn.it/~pavel/om2015/
  %papers/om2015_proceedings.pdf#page=125
  \end{tabular}
  \end{table}
  %\subsection{Jaccard}
  %TBD
  \subsection{Examples to illustrate the differences}
  TBD

>>>>

 \section*{Summary}
 %TODO Definitions
 %TODO Word index
 %TODO spelling (database dataset)
 %TODO volgorde bieb (APA?)
 %TODO Results interpretation: uitleg waarom hoger en lager
 %TODO Plaatje VOWL
 %TODO Verbeteringen discussieren
 %TODO Verwijder ensemble uit evaluation
 %TODO F-measure aan evaluation
 \tableofcontents
 \newpage

@@

  \begin{figure}
%  \includegraphics[width=0.7\textwidth]{vowlview}
  \caption[]{}
  \label{vowlfig}
  \end{figure}

@@

  \subsection{F-score}
  \begin{table}[H]
  \caption[$F_1$ mice]{The $F_1$-scores for the different matchers for the mice dataset compared to the result of AML at OAEI 2015 \cite{oaei2015}}
  \label{fscores}
  \begin{tabular}{l|ll}
  \multirow{2}{*}{\textbf{Matcher}} & \multicolumn{2}{c}{\textbf{$F_1$-score}} \\
  & Anatomy & Medical\\
  \hline
  Label Match & 0.6926 & 0.4905 \\
  Random & 0.6926 & 0.4905 \\
  Generic & 0.6372 & 0.3874 \\
  Bidirectional & 0.8432 & 0.4946 \\
  Deepwalk &  & 0.4906 \\
  Alternative & 0.6372 & 0.4905 \\
  \textbf{AML ensemble} & \textbf{0.94} & \textbf{0.81} \\ %http://disi.unitn.it/~pavel/om2015/
  %papers/om2015_proceedings.pdf#page=125
  \end{tabular}
  \end{table}
  %\subsection{Jaccard}
  %TBD
  \subsection{Examples to illustrate the differences}
  TBD
